A Comparison of Graph Processing Systems

### 2020-08-21 documentation/paper/main.tex
Introduction
add matrikelnumber and mail to paper
ligra writeup
bfs plots and some text for testing methods/results

\usepackage[noadjust]{cite}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{textcomp}
\usepackage{pifont}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\newcommand*\rot{\rotatebox{90}}
\newcommand*\OK{\ding{51}}

@@

\author{\IEEEauthorblockN{Simon König}
\IEEEauthorblockA{(3344789)\\
st156571@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Leon Matzner}
\IEEEauthorblockA{(3315161)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Felix Rollbühler}
\IEEEauthorblockA{(3310069)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Jakob Schmid}
\IEEEauthorblockA{()\\
@stud.uni-stuttgart.de}}

@@

\section{Introduction}

>>>>

\usepackage[noadjust]{cite}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{textcomp}
\usepackage{pifont}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}

\usepackage{tabularx}
\def\tabularxcolumn#1{m{#1}} % vertical centering in tabularx cells
\newcolumntype{Y}{>{\centering\arraybackslash}X} % cell type Y for centered text with automatic line breaks
\newcommand*\rot{\rotatebox{90}} % rotates content 90deg ccw, mainly for table headers
\newcommand*\OK{\ding{51}} % a checkmark-style sign

@@

\author{\IEEEauthorblockN{Simon König}
\IEEEauthorblockA{(3344789)\\
st156571@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Leon Matzner}
\IEEEauthorblockA{(3315161)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Felix Rollbühler}
\IEEEauthorblockA{(3310069)\\
st154960@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Jakob Schmid}
\IEEEauthorblockA{(3341630)\\
@stud.uni-stuttgart.de}}

@@

\section{Introduction}
%\todo
In recent years graph sizes have increased significantly, thus performance and memory efficiency of the graph analysis applications is now more important than ever.

### 2020-08-21 documentation/paper/sections/results/results.tex
new plots with std deviation
bfs plots and some text for testing methods/results

\subsection{Komplexität Aufsetzen}
Systeme wie Galois/Gluon, bei denen man erstmal ewig suchen muss bis man überhaupt einen Guide findet sollten hier schlechter abschneiden. \emph{vorausgesetzt, wir nehmen das hier überhaupt mit auf..}

\subsection{Komplexität eigene Apps schreiben}
Schwierig objektiv zu vergleichen.

@@

\subsection{Ergebnisse Calc time}
\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeSSSP.png}
	\caption{Calculation times for SSSP on a single node}
	\label{fig:ssspSingleNode}
\end{figure}
der offensichtliche, wichtige Vergleich

\subsection{Ergebnisse exec time}

>>>>

\subsection{The frameworks during setup and benchmark}
We would like to raise some issues we encountered first while installing and configuring and second while running the different frameworks.

\begin{enumerate}
	\item During setup of Gemini, we realized that the cloned repository contained several bugs, rendering the code as-is unable to perform any calculations. We had to fork and modify the source code. TODO(Was genau ging nicht, was haben wir geändert?)

	The repository with our changes can be found \href{https://github.com/jasc7636/GeminiGraph}{here}\footnote{\url{https://github.com/jasc7636/GeminiGraph}}.
	\item Furthermore, we would like to address the setup of Hadoop for Giraph. It requires multiple edits in \texttt{xml} files that aren't easily automized. This makes the setup rather time consuming, especially if reconfiguration is needed later on.
	\item Also in order for Giraph to run, several Java tasks have to be constantly running in the background. While we don't expect this to have a noticeable performance impact on other tasks, it is still not optimal.
	\item The Hadoop distributed file system (HDFS) ran us into disk space problems on multiple occasions. First, unless configured otherwise, the standard implementation replicates all data three times, distributed over all participating nodes. Second, deleting files on the HDFS does not immediately free up disk space because the files are moved to a \emph{recycling bin}-like location.

	\item 
\end{enumerate}

On a plus side, setup of frameworks like Polymer or Ligra was straight forward and did not require any special treatment.

@@

\subsection{Ergebnisse Calc time}
\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeSSSP_calcTime.png}
	\caption{Calculation times for SSSP on a single node}
	\label{fig:singleNodeSSSP_calc}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeBFS_calcTime.png}
	\caption{Calculation times for BFS on a single node}
	\label{fig:singleNodeBFS_calc}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeSSSPGaloisThreads.png}
	\caption{Calculation times of Galois' SSSP over the thread count}
	\label{fig:singleNodeSSSPGaloisThreads}
\end{figure}

\subsection{Ergebnisse exec time}
\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeSSSP_execTime.png}
	\caption{Execution times for SSSP on a single node}
	\label{fig:singleNodeSSSP_exec}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeSSSP_overheadTimeNormalized.png}
	\caption{Normalized Overhead SSSP single node}
	\label{fig:singleNodeSSSP_overheadNormalized}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeSSSP_overheadTime.png}
	\caption{Overhead SSSP single node}
	\label{fig:singleNodeSSSP_overhead}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeBFS_execTime.png}
	\caption{Execution times for BFS on a single node}
	\label{fig:singleNodeBFS_exec}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeBFS_overheadTime.png}
	\caption{Overhead BFS single node}
	\label{fig:singleNodeBFS_overhead}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeBFS_overheadTimeNormalized.png}
	\caption{Normalized Overhead BFS single node}
	\label{fig:singleNodeBFS_overheadNormalized}
\end{figure}

### 2020-08-21 documentation/paper/sections/testingMethods.tex
new plots with std deviation
bfs plots and some text for testing methods/results

All benchmarks were initiated by our benchmark script that is available in our repository. Galois, Gemini and Giraph were benchmarked on both the 5-node cluster and a singe machine.
Furthermore, -- since Galois supports this parameter -- we ran multiple tests comparing Galois' performance with different core counts on a single machine.

@@

\subsection{Algorithms}
We ran Breadth-first search (BFS), PageRank (PR) and Single-source shortest-path (SSSP) algorithms on each framework and graph.
For frameworks that support multiple implementations (e.g. PageRank in push and pull modes), we included the alternatives in our testing.

\begin{table}
	\caption{Natively supported algorithms of the Frameworks}
	\label{tbl:algorithms}
	\centering
	\begin{tabular}{ccccccc}
		\multicolumn{2}{c}{\bf{Algorithm}}&\rot{Galois}&\rot{Gemini}&\rot{Giraph}&\rot{Ligra}&\rot{Polymer}\\\hline
		\multirow{3}{*}{\rot{PageRank}}	&Push&\OK&&&?&\OK\\
										&Pull&\OK&&&?&\\
										&Delta&?&&&\OK&\OK\\
		\hline
	\end{tabular}
\end{table}

@@

\subsection{Implementing new application}

>>>>

All benchmarks were initiated by our benchmark script that is available in our repository. Galois, Gemini and Giraph were benchmarked on both the 5-node cluster and a singe machine.
Since Galois supports this parameter, we ran multiple tests comparing Galois' performance with different thread counts on a single machine.

@@

\subsection{Algorithms}
We ran Breadth-first search (BFS), PageRank (PR) and Single-source shortest-path (SSSP) algorithms on each framework and graph.
For frameworks that support multiple implementations (e.g. PageRank in push and pull modes), we included the alternatives in our testing. 
\autoref{tbl:algorithms} shows the tested algorithms in detail.
\newcommand{\txtdag}{\textsuperscript{\textdagger}}
\begin{table}
	\caption{Tested algorithms of the frameworks}
	\label{tbl:algorithms}
	\centering
	\begin{tabularx}{\columnwidth}{cYYYYY}
		\bf{Algorithm}&\rot{Galois}&\rot{Gemini}&\rot{Giraph}&\rot{Ligra}&\rot{Polymer}\\\hline
		PageRank&$\Delta$Push, $\Delta$Pull&&&&\\
		SSSP&?, Push, Pull&&&&\\
		BFS&Yes&&*&&\\
		\hline
	\end{tabularx}

	* Algorithm not natively supported

\end{table}

@@
